### 2024-08-10 mixed-models.qmd
20240810 - clean up

@@

#mgcv smooth terms: https://stat.ethz.ch/R-manual/R-devel/library/mgcv/html/smooth.terms.html

#bayesianMixedModelFormula <- brms::bf(
#  fantasy_points ~ positionFactor + s(ageCentered20, by = #positionFactor) + years_of_experience + s(ageCentered20, #player_idFactor, bs = "fs") + (1 | player_idFactor)
#)

#bayesianMixedModelFormula <- brms::bf(
#  fantasy_points ~ positionFactor + s(ageCentered20, by = #positionFactor) + years_of_experience + (1 | player_idFactor)
#)

>>>>

Information about smooth terms in the `mgcv` package is provided at the following link: <https://stat.ethz.ch/R-manual/R-devel/library/mgcv/html/smooth.terms.html>.

@@
